
### Key metrics

```{r}
#| label: key_metrics
#| results: 'asis'
key_tables <-
  key_metric_table(es_data, detailed = FALSE)

is_hashed_experiment <- "pool" %in% names(es_data$samplesheet)
has_key_metrics <-
  !is.null(key_tables$pool) || !is.null(key_tables$sample)
eval_hashed_key_metrics <- is_hashed_experiment && has_key_metrics
eval_standard_key_metrics <-
  !is_hashed_experiment && !is.null(key_tables$sample)
```

```{r}
#| label: key_metrics_pool
#| eval: !expr eval_hashed_key_metrics
#| results: 'asis'
open_tabset()
if (!is.null(key_tables$pool)) {
  section_table(key_tables$pool, "Hash pool metrics", 3)
}
if (!is.null(key_tables$sample)) {
  section_table(key_tables$sample, "Sample metrics", 3)
}
close_tabset()
```

```{r}
#| label: key_metrics_sample
#| eval: !expr eval_standard_key_metrics
#| results: 'asis'
section_table(key_tables$sample, "Sample metrics", 3)
```

```{r}
#| label: sample_hashing_section_intro
#| eval: !expr is_hashed_experiment
#| results: 'asis'
section_intro(
  "Sample hashing",
  glue::glue(
    "The hash purity for an antibody is defined as the number of UMIs from the most common ",
    "antibody hash divided by the sum of UMIs for all antibody hashes. For instance, if B2M-1 ",
    "is the most common hash, the hash purity for B2M is the number of UMIs for B2M-1 divided ",
    "by the sum of UMIs for all B2M hashes.\n\n"
  ),
  3
)
```

```{r}
#| label: sample_hashing
#| eval: !expr is_hashed_experiment
#| results: 'asis'
component <-
  component_hashing(es_data, colors = cherry_gradient)

tabset_figure_table(
  component$plot,
  component$table,
  level = 4
)
close_tabset()

tabset_plotlist(component$sample_confidence_plots, level = 4)
```

### Sequencing

#### Sequencing saturation

Sequencing saturation is the fraction of a library's complexity that has been
captured through sequencing.

```{r}
#| label: qc_metrics_sequencing_saturation
#| results: 'asis'
if (params$debug_mode) {
  seqsat_comps <- 5L
} else {
  seqsat_comps <- 100L
}
set.seed(123)

plots <-
  component_sequencing_saturation_curve(
    es_data,
    seqsat_comps = seqsat_comps
  )

tabset_plotlist(plots,
  level = 5
)
```

#### Reads and molecules

Here we review the number of reads per stage of the `pixelator` pipeline, and the number of molecules that they are
mapped to.

```{r}
#| label: qc_metrics_reads
#| fig-height: 4
#| results: 'asis'
component <-
  component_sequencing_reads_and_molecules(es_data)

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5
)
close_tabset()
```

#### Reads per cell

```{r}
#| label: qc_metrics_reads_per_cell
#| results: 'asis'
component <-
  component_sequencing_reads_per_cell(es_data)

tabset_figure_table(
  component$plot,
  component$table,
  level = 5
)
close_tabset()
```

### Cell recovery

#### Number of components

The molecule rank plot below ranks the components of a sample from the most to the fewest molecules. Cells appear as
the plateau of large components to the left, and the curve drops where cells give way to background components such as
debris. A sharp drop means that cells are well separated from background, while a gradual slope means that the two are
harder to tell apart. The dashed lines mark the minimum and maximum component size thresholds, and only components
between them are kept as cells.

```{r}
#| label: qc_metrics_molrank_plot
#| results: 'asis'

component <-
  component_cell_recovery(es_data)

tabset_figure_table(
  component$plots[[2]],
  component$table[[2]],
  level = 5, mode = "tabset_nested"
)
close_tabset()
```

```{r}
#| label: qc_metrics_molecule_count
#| results: 'asis'
component_molecule_plot(es_data, sample_palette)
```

### Graph metrics

#### k-coreness

k-coreness is a measure of the connectivity of a node in a graph. A node with a
high k-coreness is well connected to
other nodes in the graph.

```{r}
#| label: qc_metrics_nodes_kcore
#| results: 'asis'
component <-
  component_coreness(es_data)

tabset_figure_table(
  component$plots[[1]],
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

#### Denoising

Denoising removes low-connectivity graph nodes to improve data quality.

```{r}
#| label: qc_metrics_denoising
#| results: 'asis'
component <-
  component_denoising(es_data)

tabset_figure_table(
  component$plots$removed_umis,
  component$tables$removed_umis,
  level = 5,
  mode = "title"
)
close_tabset()
```

### Isotype control markers

```{r}
#| label: qc_metrics_frac_control
#| results: 'asis'
component <- component_control_markers(es_data)

tabset_figure_table(
  component$p1,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```
