---
execute:
  dev: ragg_png
  execute-dir: dir
  echo: false
  warning: false
  message: false
  error: true
---

### Dimensionality Reduction 

```{r}
#| label: dimred_plots
#| results: 'asis'
#| fig-height: 5
component <-
  component_dimred_plots(
    pg_data_processed,
    plot_reductions = preferred_dimred_order(Reductions(pg_data_processed)),
    sample_palette = sample_palette,
    cluster_palette = cluster_palette,
    sample_plots = TRUE,
    plot_height = 5
  )

tabset_nested_plotlist(component, level = 3)
```

### Cell Annotation 

::: {.callout-warning}

The Proxiome Experiment Summary performs automatic cell annotation by matching each cell’s protein profile to annotated 
cells in a reference PBMC dataset. These automated labels should be interpreted with caution, particularly when the 
sample composition differs substantially from the PBMC reference. In such cases, for example in certain stimulated 
samples or cell lines, the annotations may be unreliable. We therefore recommend performing cell annotation as part of 
downstream analysis to ensure accurate and context-appropriate results.

:::

::: {.panel-tabset .nav-pills}

#### Cell type fractions

```{r}
#| label: annotation_dimred
#| results: 'asis'
component <-
  component_annotation(pg_data_processed,
    heatmap_gradient = cherry_gradient
  )
```

```{r}
#| label: annotation_summary
#| fig-height: 4
#| results: 'asis'

tabset_figure_table(
  component$celltype_composition,
  component$celltype_composition_table,
  level = 5
)
close_tabset()
```


```{r}
#| label: annotation_summary2
#| fig-height: 4
#| results: 'asis'
tabset_plotlist(component$celltype_composition_barplots1, level = 5)
```


```{r}
#| label: annotation_summary3
#| fig-height: 4
#| results: 'asis'
tabset_plotlist(component$celltype_composition_barplots2, level = 5)
```

#### UMAP 

```{r}
#| label: annotation_umap
#| fig-height: 4
#| results: 'asis'

tabset_plotlist(component$dimred_plots, level = 5)
```

#### Cluster abundance heatmap

```{r}
#| label: annotation_dimred_heatmap
#| fig-height: 17
#| results: 'asis'
component$heatmap
```

:::
