---
title: "Experiment Summary"
subtitle: "v0.3.0" 
format:
  html:
    theme: cerulean
    page-layout: full
    embed-resources: true
    code_folding: show
    fig-width: 8
    fig-height: 5
    fig-dpi: 150
    css: styles.css
knitr:
  opts_chunk:
    out.width: "100%"
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
execute:
  execute-dir: dir
  echo: false
  warning: false
  message: false
params: 
  
  sample_sheet: "../../../ES_test_data/test_samplesheet.csv"
  data_folder: "../../../ES_test_data/"
  control_markers: ["mIgG1", "mIgG2a", "mIgG2b"]
  do_harmonize: FALSE
  harmonization_vars: ["condition"]
  norm_method: "CLR"
  clustering_resolution: 1
  annotation_method: "Seurat"
  mc_cores: 1
  debug_mode: FALSE
  test_mode: FALSE
---

# 

::: {.panel-tabset .nav-pills}

```{r load_packages, include = FALSE}
library(pixelatorES)
library(pixelatorR)
library(Seurat)
library(dplyr)
library(tibble)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggplotify)
library(purrr)
```
  
## Samples 

Here, we set the sample name and the path to the data files. 


```{r}
#| label: samples
#| results: 'asis'
sample_sheet <-
  read_samplesheet(params$sample_sheet)

sample_aliases <-
  sample_sheet %>%
  select(sample, sample_alias) %>%
  deframe()

print_metadata_table(sample_sheet)
```


```{r}
#| label: theme
#| include: false
heatmap_gradient <-
  PixelgenGradient(100, "BluesCherry")

cherry_gradient <-
  PixelgenGradient(100, "Cherry")

sample_palette <- create_sample_palette(sample_sheet$condition)
```

```{r}
#| label: read_counts
file_paths <- get_file_paths(
  data_folder = params$data_folder,
  sample_aliases = sample_aliases
)

data_files <- file_paths$data_files
qc_files <- file_paths$qc_files

pg_data <-
  load_pxl_data_list(params$data_folder, data_files, sample_sheet) %>%
  merge_data(sample_sheet)

if (params$debug_mode) {
  pg_data <-
    downsample_data(pg_data,
      control_markers = params$control_markers,
      n_cells = 50,
      n_markers = 21
    )
}
```

## Quality metrics

```{r}
#| label: read_qc_metrics
#| results: 'asis'
sample_qc_metrics <-
  read_qc_files(qc_files, sample_sheet)

qc_metrics_tables <-
  get_qc_metrics(pg_data, sample_qc_metrics, sample_sheet)
```

### Key metrics

```{r}
#| label: key_metrics
#| results: 'asis'
key_metric_table(qc_metrics_tables)
```


### Sequencing
#### Reads and molecules 

Here we review the number of reads per stage of the `pixelator` pipeline, and the number of molecules that they are 
mapped to.

```{r}
#| label: qc_metrics_reads
#| fig-height: 4
#| results: 'asis'
component <-
  component_sequencing_reads_and_molecules(sample_qc_metrics)

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5
)
close_tabset()
```

#### Sequencing saturation 

Sequencing saturation is the fraction of a library's complexity that has been 
captured through sequencing.

```{r}
#| label: qc_metrics_sequencing_saturation
#| results: 'asis'

component <-
  component_sequencing_saturation(
    qc_metrics_tables,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

### Cell recovery

#### Number of components 

```{r}
#| label: qc_metrics_component_count
#| results: 'asis'
component <-
  component_cell_recovery(sample_qc_metrics,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot[[1]],
  component$table[[1]],
  level = 5
)
close_tabset()
```


```{r}
#| label: qc_metrics_molecule_count
#| results: 'asis'
component_molecule_plot(pg_data, sample_palette)
```


```{r}
#| label: qc_metrics_molrank_plot
#| results: 'asis'
tabset_figure_table(
  component$plot[[2]],
  component$table[[2]],
  level = 5
)
close_tabset()
```


### Graph metrics

#### A/B node degree 

The mean degree of A and B nodes. 

```{r}
#| label: qc_metrics_ab_node_degree
#| results: 'asis'
component <-
  component_node_degree(pg_data,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot,
  component$table,
  level = 5
)
close_tabset()
```

#### Crossing edges 

In the `graph` stage of the `pixelator` pipeline, components corresponding to 
cells are identified by finding parts of the graph with high intraconnectivity. 
These components recovered from the graph by removing a low number of presumed 
random edges that are known as "crossing edges".

```{r}
#| label: qc_metrics_crossing_edges
#| results: 'asis'
component <-
  component_crossing_edges(qc_metrics_tables,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot,
  component$tabl,
  level = 5
)
close_tabset()
```

#### k-coreness 

k-coreness is a measure of the connectivity of a node in a graph. A node with a 
high k-coreness is well connected to 
other nodes in the graph.

```{r}
#| label: qc_metrics_nodes_kcore
#| results: 'asis'
component <-
  component_coreness(qc_metrics_tables)

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```


```{r}
#| label: qc_metrics_nodes_kcore_heatmap
#| fig-height: 3
#| results: 'asis'
tabset_plotlist(component$heatmap_plots, level = 5)
```

### Bleedover noise

```{r}
#| label: qc_metrics_bleedover_ratio
#| results: 'asis'
component_bleedover_noise(qc_metrics_tables) %>% print()
```

### Control markers 

```{r}
#| label: qc_metrics_frac_control
#| results: 'asis'
component <- component_control_markers(pg_data)

tabset_figure_table(
  list(component$p1, component$p2),
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

```{r}
#| label: qc_metrics_cleanup
rm(sample_qc_metrics)
```

```{r}
#| label: cell_processing
#| include: false

pg_data_processed <- process_data(pg_data, params)

rm(pg_data)
```

## Cell annotation

```{r}
#| label: dimred_plots
#| fig-height: 4
#| results: 'asis'
component <-
  component_dimred_plots(
    pg_data_processed,
    plot_reductions = preferred_dimred_order(Reductions(pg_data_processed)),
    sample_palette = sample_palette,
    cluster_palette = unname(cell_palette),
    sample_plots = FALSE
  )

tabset_nested_plotlist(component, level = 3)
```

We run an automatic annotation using an annotated reference dataset. This allows
us to put a few simple labels on cell populations, which can be useful for 
downstream analysis. We visualize the annotation using UMAPs 
(integrated and not).

::: {.panel-tabset .nav-pills}

### Automated annotation

```{r}
#| label: annotation_dimred
#| results: 'asis'
component <-
  component_annotation(pg_data_processed,
    heatmap_gradient = cherry_gradient
  )

tabset_plotlist(component$dimred_plots, level = 4)
```


```{r}
#| label: annotation_dimred_heatmap
#| fig-height: 16
#| results: 'asis'
component$heatmap
```

### Summary

```{r}
#| label: annotation_summary
#| fig-height: 4
#| results: 'asis'
component$celltype_composition
```


```{r}
#| label: annotation_summary2
#| fig-height: 4
#| results: 'asis'
tabset_plotlist(component$celltype_composition_barplots1, level = 4)
```


```{r}
#| label: annotation_summary3
#| fig-height: 4
#| results: 'asis'
tabset_plotlist(component$celltype_composition_barplots2, level = 4)
```


```{r}
#| label: annotation_summary4
#| fig-height: 4
#| results: 'asis'
component$celltype_composition_table
```

:::

## Abundance 

::: {.panel-tabset .nav-pills}

### Global 

```{r}
#| label: global_abundance_per_marker
#| fig-height: 4
#| results: 'asis'
plots <- component_abundance_per_sample(pg_data_processed, params, sample_palette, sample_aliases, params$test_mode)

tabset_plotlist(plots, level = 5)
```

### Per celltype 

```{r}
#| label: per_celltype_abundance
#| fig-height: 4
#| results: 'asis'
plots <- component_abundance_per_celltype(pg_data_processed, params, sample_palette, params$test_mode)

tabset_plotlist(plots, level = 5)
```

:::


## Proximity

::: {.panel-tabset .nav-pills}

```{r}
#| label: global_proximity_load
#| results: 'asis'
proximity_scores <- filter_proximity_scores(pg_data_processed, params, sample_levels = sample_aliases)
```

### Self-proximity 

::: {.panel-tabset .nav-pills}

#### Per marker

```{r}
#| label: global_proximity_per_marker
#| fig-height: 4
#| results: 'asis'
processed_data <-
  proximity_scores %>%
  filter(as.character(marker_1) == as.character(marker_2)) %>%
  group_by(marker_1)
```

```{r}
#| label: global_proximity_per_marker_logratio
#| fig-height: 4
#| results: 'asis'
plots <- component_proximity_per_marker(processed_data, "log2_ratio", sample_palette, params$test_mode)
tabset_plotlist(plots, level = 5)
```

#### Per celltype 

```{r}
#| label: polarity_summary
#| fig-width: 16
#| fig-height: 6
plots <- component_clustering_summary(proximity_scores, heatmap_gradient, params$test_mode)
print(plots$log2_ratio)
```

:::


### Colocalization 
::: {.panel-tabset .nav-pills}

#### Global 

```{r}
#| label: coloc_global_summary
#| results: 'asis'
processed_data <- summarize_colocalization_scores_per_sample(proximity_scores, params$test_mode)
```

```{r}
#| label: coloc_global_summary_heatmap_logratio
#| fig-width: 14
#| fig-height: 10
#| results: 'asis'
plots <- component_proximity_heatmap_sample(processed_data, heatmap_gradient, "log2_ratio")
tabset_plotlist(plots, level = 5)
```



#### Per Celltype 

```{r}
#| label: coloc_celltype_summary
#| fig-width: 14
#| fig-height: 10
#| results: 'asis'
processed_data <- summarize_colocalization_scores_per_celltype(proximity_scores, params$test_mode)
```

```{r}
#| label: coloc_celltype_summary_heatmap_logratio
#| fig-width: 14
#| fig-height: 10
#| results: 'asis'
plots <- component_proximity_heatmap_celltype(processed_data, heatmap_gradient, "log2_ratio")
tabset_plotlist(plots, level = 5)
```

:::

:::

## Run settings

```{r}
#| label: run_settings
# Print parameters
print_params(params)

# Print session info
print_session_info()
```


:::
