
### Key metrics

```{r}
#| label: key_metrics
#| results: 'asis'
key_tables <-
  key_metric_table(qc_metrics_tables, detailed = isTRUE(params$key_metrics_detailed))

eval_pool_tables <-
  isTRUE(params$include_pool_hash_metrics) && !is.null(key_tables$pool)
eval_standard_results <- !eval_pool_tables
```

```{r}
#| label: key_metrics_pool
#| eval: !expr eval_pool_tables
#| results: 'asis'
cat("::: {.panel-tabset .nav-pills}\n")
section_table(key_tables$pool, "Hash pool metrics", 3)
section_table(key_tables$sample, "Sample metrics", 3)
cat(":::\n")
```

```{r}
#| label: key_metrics_sample
#| eval: !expr eval_standard_results
#| results: 'asis'
section_table(key_tables$sample, "Sample metrics", 3)
```

```{r}
#| label: sample_hashing_section_intro
#| eval: !expr eval_pool_tables && isTRUE(params$include_sample_hashing_section)
#| results: 'asis'
section_intro(
  "Sample hashing",
  glue::glue(
    "The hash purity for an antibody is defined as the number of UMIs from the most common ",
    "antibody hash divided by the sum of UMIs for all antibody hashes. For instance, if B2M-1 ",
    "is the most common hash, the hash purity for B2M is the number of UMIs for B2M-1 divided ",
    "by the sum of UMIs for all B2M hashes.\n\n"
  ),
  3
)
```

```{r}
#| label: sample_hashing
#| eval: !expr eval_pool_tables && isTRUE(params$include_sample_hashing_section)
#| results: 'asis'
component <-
  component_hashing(qc_metrics_tables)

tabset_figure_table(
  component$plot,
  component$table,
  level = 4
)
close_tabset()
```

```{r}
#| label: qc_metrics_nodes_hash_purity_heatmap
#| eval: !expr eval_pool_tables && isTRUE(params$include_sample_hashing_section)
#| fig-height: 3
#| results: 'asis'
tabset_plotlist(component$heatmap_plots_hash_purity, level = 4)
```

```{r}
#| label: qc_metrics_nodes_hash_fraction_heatmap
#| eval: !expr eval_pool_tables && isTRUE(params$include_sample_hashing_section)
#| fig-height: 3
#| results: 'asis'
tabset_plotlist(component$heatmap_plots_hash_fraction, level = 4)
```

### Sequencing

#### Reads and molecules

Here we review the number of reads per stage of the `pixelator` pipeline, and the number of molecules that they are
mapped to.

```{r}
#| label: qc_metrics_reads
#| fig-height: 4
#| results: 'asis'
component <-
  component_sequencing_reads_and_molecules(
    sample_qc_metrics,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5
)
close_tabset()
```

#### Sequencing saturation

Sequencing saturation is the fraction of a library's complexity that has been
captured through sequencing.

```{r}
#| label: qc_metrics_sequencing_saturation
#| results: 'asis'
if (params$debug_mode) {
  seqsat_comps <- 1L
} else {
  seqsat_comps <- 5L
}

plots <-
  component_sequencing_saturation_curve(
    pg_data,
    data_files,
    seqsat_comps = seqsat_comps,
    sample_levels = sample_aliases,
    mc_cores = params$mc_cores
  )

tabset_plotlist(plots,
  level = 5
)

component <-
  component_sequencing_saturation(
    qc_metrics_tables,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

#### Reads per cell

```{r}
#| label: qc_metrics_reads_per_cell
#| results: 'asis'
component <-
  component_sequencing_reads_per_cell(pg_data)

tabset_figure_table(
  component$plot,
  component$table,
  level = 5
)
close_tabset()
```

### Cell recovery

#### Number of components

```{r}
#| label: qc_metrics_component_count
#| results: 'asis'
component <-
  component_cell_recovery(
    sample_qc_metrics,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot[[1]],
  component$table[[1]],
  level = 5
)
close_tabset()
```

```{r}
#| label: qc_metrics_molecule_count
#| results: 'asis'
component_molecule_plot(pg_data, sample_palette)
```

```{r}
#| label: qc_metrics_molrank_plot
#| results: 'asis'
tabset_figure_table(
  component$plot[[2]],
  component$table[[2]],
  level = 5
)
close_tabset()
```

### Graph metrics

#### A/B node degree

The mean degree of A and B nodes.

```{r}
#| label: qc_metrics_ab_node_degree
#| results: 'asis'
component <-
  component_node_degree(pg_data,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot,
  component$table,
  level = 5
)
close_tabset()
```

#### Crossing edges

In the `graph` stage of the `pixelator` pipeline, components corresponding to
cells are identified by finding parts of the graph with high intraconnectivity.
These components recovered from the graph by removing a low number of presumed
random edges that are known as "crossing edges".

```{r}
#| label: qc_metrics_crossing_edges
#| results: 'asis'
component <-
  component_crossing_edges(
    qc_metrics_tables,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot,
  component$tabl,
  level = 5
)
close_tabset()
```

#### k-coreness

k-coreness is a measure of the connectivity of a node in a graph. A node with a
high k-coreness is well connected to
other nodes in the graph.

```{r}
#| label: qc_metrics_nodes_kcore
#| results: 'asis'
component <-
  component_coreness(qc_metrics_tables)

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

```{r}
#| label: qc_metrics_nodes_kcore_heatmap
#| fig-height: 3
#| results: 'asis'
tabset_plotlist(component$heatmap_plots, level = 5)
```

### Bleedover noise

```{r}
#| label: qc_metrics_bleedover_ratio
#| results: 'asis'
component_bleedover_noise(qc_metrics_tables) %>% print()
```

### Control markers

```{r}
#| label: qc_metrics_frac_control
#| results: 'asis'
component <- component_control_markers(pg_data)

tabset_figure_table(
  list(component$p1, component$p2),
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

```{r}
#| label: qc_metrics_cleanup
rm(sample_qc_metrics)
```
