
### Key metrics

```{r}
#| label: key_metrics
#| results: 'asis'
key_tables <-
  key_metric_table(qc_metrics_tables, detailed = FALSE)

eval_standard_results_and_sample_hashing <-
  !is.null(key_tables$pool)
eval_standard_results <- !eval_standard_results_and_sample_hashing
```

```{r}
#| label: key_metrics_pool
#| eval: !expr eval_standard_results_and_sample_hashing
#| results: 'asis'
cat("::: {.panel-tabset .nav-pills}\n")
section_table(key_tables$pool, "Hash pool metrics", 3)
section_table(key_tables$sample, "Sample metrics", 3)
cat(":::\n")
```

```{r}
#| label: key_metrics_sample
#| eval: !expr eval_standard_results
#| results: 'asis'
section_table(key_tables$sample, "Sample metrics", 3)
```

```{r}
#| label: sample_hashing_section_intro
#| eval: !expr eval_standard_results_and_sample_hashing
#| results: 'asis'
section_intro(
  "Sample hashing",
  glue::glue(
    "The hash purity for an antibody is defined as the number of UMIs from the most common ",
    "antibody hash divided by the sum of UMIs for all antibody hashes. For instance, if B2M-1 ",
    "is the most common hash, the hash purity for B2M is the number of UMIs for B2M-1 divided ",
    "by the sum of UMIs for all B2M hashes.\n\n"
  ),
  3
)
```

```{r}
#| label: sample_hashing
#| eval: !expr eval_standard_results_and_sample_hashing
#| results: 'asis'
component <-
  component_hashing(qc_metrics_tables, colors = cherry_gradient)

tabset_figure_table(
  component$plot,
  component$table,
  level = 4
)
close_tabset()

tabset_plotlist(component$sample_confidence_plots, level = 4)
```

### Sequencing

#### Sequencing saturation

Sequencing saturation is the fraction of a library's complexity that has been
captured through sequencing.

```{r}
#| label: qc_metrics_sequencing_saturation
#| results: 'asis'
if (params$debug_mode) {
  seqsat_comps <- 5L
} else {
  seqsat_comps <- 100L
}
set.seed(123)

plots <-
  component_sequencing_saturation_curve(
    pg_data,
    data_files,
    seqsat_comps = seqsat_comps,
    sample_levels = sample_aliases
  )

tabset_plotlist(plots,
  level = 5
)
```

#### Reads and molecules

Here we review the number of reads per stage of the `pixelator` pipeline, and the number of molecules that they are
mapped to.

```{r}
#| label: qc_metrics_reads
#| fig-height: 4
#| results: 'asis'
component <-
  component_sequencing_reads_and_molecules(
    sample_qc_metrics,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5
)
close_tabset()
```

#### Reads per cell

```{r}
#| label: qc_metrics_reads_per_cell
#| results: 'asis'
component <-
  component_sequencing_reads_per_cell(pg_data)

tabset_figure_table(
  component$plot,
  component$table,
  level = 5
)
close_tabset()
```

### Cell recovery

#### Number of components

```{r}
#| label: qc_metrics_molrank_plot
#| results: 'asis'

component <-
  component_cell_recovery(
    pg_data,
    sample_qc_metrics,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plots[[2]],
  component$table[[2]],
  level = 5, mode = "tabset_nested"
)
close_tabset()
```

```{r}
#| label: qc_metrics_molecule_count
#| results: 'asis'
component_molecule_plot(pg_data, sample_palette)
```

### Graph metrics

#### k-coreness

k-coreness is a measure of the connectivity of a node in a graph. A node with a
high k-coreness is well connected to
other nodes in the graph.

```{r}
#| label: qc_metrics_nodes_kcore
#| results: 'asis'
component <-
  component_coreness(qc_metrics_tables)

tabset_figure_table(
  component$plots[[1]],
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

#### Denoising

Denoising removes low-connectivity graph nodes to improve data quality.

```{r}
#| label: qc_metrics_denoising
#| results: 'asis'
component <-
  component_denoising(qc_metrics_tables, sample_levels = sample_aliases)

tabset_figure_table(
  component$plots$removed_umis,
  component$tables$removed_umis,
  level = 5,
  mode = "title"
)
close_tabset()
```

### Control markers

```{r}
#| label: qc_metrics_frac_control
#| results: 'asis'
component <- component_control_markers(pg_data)

tabset_figure_table(
  component$p1,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

```{r}
#| label: qc_metrics_cleanup
rm(sample_qc_metrics)
```
