
### Key metrics

```{r}
#| label: key_metrics
#| results: 'asis'
key_metric_table(qc_metrics_tables, detailed = FALSE)
```


### Sequencing

#### Sequencing saturation 

Sequencing saturation is the fraction of a library's complexity that has been 
captured through sequencing.

```{r}
#| label: qc_metrics_sequencing_saturation
#| results: 'asis'

if (params$debug_mode) {
  seqsat_comps <- 1L
} else {
  seqsat_comps <- 5L
}

plots <-
  component_sequencing_saturation_curve(
    pg_data,
    data_files,
    seqsat_comps = seqsat_comps,
    sample_levels = sample_aliases,
    mc_cores = params$mc_cores
  )

tabset_plotlist(plots,
  level = 5
)
```

#### Reads and molecules 

Here we review the number of reads per stage of the `pixelator` pipeline, and the number of molecules that they are 
mapped to.

```{r}
#| label: qc_metrics_reads
#| fig-height: 4
#| results: 'asis'
component <-
  component_sequencing_reads_and_molecules(sample_qc_metrics)

tabset_figure_table(
  component$plots,
  component$tabl,
  level = 5
)
close_tabset()
```


```{r}
#| label: qc_metrics_reads_per_cell
#| results: 'asis'

component <-
  component_sequencing_reads_per_cell(pg_data)

tabset_figure_table(
  component$plot,
  component$table,
  level = 5
)
close_tabset()
```


### Cell recovery

#### Number of components 

```{r}
#| label: qc_metrics_molrank_plot
#| results: 'asis'

component <-
  component_cell_recovery(sample_qc_metrics,
    sample_levels = sample_aliases
  )

tabset_figure_table(
  component$plot[[2]],
  component$table[[2]],
  level = 5
)
close_tabset()
```

```{r}
#| label: qc_metrics_molecule_count
#| results: 'asis'

component_molecule_plot(pg_data, sample_palette)
```

### Graph metrics

#### k-coreness 

k-coreness is a measure of the connectivity of a node in a graph. A node with a 
high k-coreness is well connected to 
other nodes in the graph.

```{r}
#| label: qc_metrics_nodes_kcore
#| results: 'asis'
component <-
  component_coreness(qc_metrics_tables)

tabset_figure_table(
  component$plots[[1]],
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

### Control markers 

```{r}
#| label: qc_metrics_frac_control
#| results: 'asis'
component <- component_control_markers(pg_data)

tabset_figure_table(
  component$p1,
  component$tabl,
  level = 5,
  mode = "title"
)
close_tabset()
```

```{r}
#| label: qc_metrics_cleanup
rm(sample_qc_metrics)
rm(pg_data)
```
