
In PNA, each cell is represented as a graph where proteins are nodes and edges reflect spatial proximity. 
For each protein pair, the observed number of edges (join count) is compared to the expected number under random 
permutations, which account for protein abundance.  

The **log2 ratio** Proximity Score summarizes this comparison as the log2-transformed ratio of observed to expected 
counts. A value of **+1** means twice as many edges as expected by chance, while **−1** means half as many. 
This provides an intuitive measure of spatial correlation, highlighting patterns such as clustering or colocalization.

Learn more at [PNA Proximity Scores](https://software.pixelgen.com/pixelator/algorithms/#pna-proximity-scores).

::: {.panel-tabset .nav-pills}

### Clustering 

```{r}
#| label: global_proximity_per_marker_logratio
#| fig-height: 8
#| results: 'asis'

plots <- component_proximity_per_marker(proximity_scores, sample_palette = sample_palette, test_mode = params$test_mode)
tabset_plotlist(plots, level = 5)
```


### Colocalization 
::: {.panel-tabset .nav-pills}

#### Global 

```{r}
#| label: coloc_global_summary_heatmap_logratio
#| fig-width: 14
#| fig-height: 10
#| results: 'asis'

plots <- component_proximity_heatmap_sample(
    proximity_scores, 
    heatmap_gradient, 
    plot_markers = proximity_top_markers, 
    test_mode = params$test_mode
    )
tabset_plotlist(plots, level = 5)
```

#### Per Celltype 

```{r}
#| label: coloc_celltype_summary_heatmap_logratio
#| fig-width: 14
#| fig-height: 10
#| results: 'asis'
plots <- component_proximity_heatmap_celltype(
    proximity_scores, 
    heatmap_gradient, 
    plot_markers = proximity_top_markers, 
    test_mode = params$test_mode
    )
tabset_nested_plotlist(plots, level = 5)
```

:::

:::
